A Safe and High-Performance Aliasing-Tolerant Parallel Programming Model

### 2012-11-14 doc/types-pldi2013/langdef.tex
two more minor tweaks

Instead we use a bottom-up approach with big-step semantics.
Each expression has a clobber set $C$ of memory locations that might 
be modified by concurrent evaluations.  Reads of locations in $C$ may be
chosen to return a value other than what was most recently written by the current
expression, as long a
valid interleaving of the operations with other concurrent operations can be found within
an enclosing expression.
%% While a read from a location not in $C$ is {\em coherent}
%% (returning the most recently written value), the value read from a location $l$ in $C$ may be any
%% value.  Determining which value is deferred until all potentially-concurrent
%% modifications to $l$ are observable in the evaluation of a parent expression whose clobber set does
%% not include $l$ and a consistent interleaving of the subexpressions' memory traces is determined.
%With this formulation, the criteria for when a hierarchical scheduler may execute subexpressions in parallel can be
%made clear, but they are no longer constructive.  Instead, we will have to show that the scheduling algorithm
%used by the Legion runtime satisfies these constraints, guaranteeing the soundness of the Legion programming model.

@@

\noindent
%We must show $\privconsist{E}{\Phi}$ holds for any execution of an expression $e$ with static privileges $\Phi$.
As usual, the soundness claim is proven assuming the initial type and execution environments are consistent.
For our results, three consistency properties are needed:
\begin{itemize}
\item mapping consistency, written $\mapconsist{\Omega}$, guarantees a region mapping $M$ satisfies the region constraints $\Omega$% under which an expression was typed
\item local value consistency, written $\localconsist{L}{\Gamma}$, guarantees local values in $L$ have types consistent with the environment $\Gamma$ (with logical regions mapped to physical regions via $M$)
%under which the expression was typed
\item store consistency, written $\storeconsist{S}{H}$, guarantees locations in $S$ have values consistent with heap typing $H$
\end{itemize}

>>>>

Instead we use a bottom-up approach with big-step semantics.
Each expression has a clobber set $C$ of memory locations that might 
be modified by concurrent evaluations.  Reads of locations in $C$ may be
chosen to return a value other than what was most recently written by the current
expression, as long as a
valid interleaving of the operations with other concurrent operations can be found within
an enclosing expression.
%% While a read from a location not in $C$ is {\em coherent}
%% (returning the most recently written value), the value read from a location $l$ in $C$ may be any
%% value.  Determining which value is deferred until all potentially-concurrent
%% modifications to $l$ are observable in the evaluation of a parent expression whose clobber set does
%% not include $l$ and a consistent interleaving of the subexpressions' memory traces is determined.
%With this formulation, the criteria for when a hierarchical scheduler may execute subexpressions in parallel can be
%made clear, but they are no longer constructive.  Instead, we will have to show that the scheduling algorithm
%used by the Legion runtime satisfies these constraints, guaranteeing the soundness of the Legion programming model.

@@

\noindent
%We must show $\privconsist{E}{\Phi}$ holds for any execution of an expression $e$ with static privileges $\Phi$.
As usual, the soundness claim is proven assuming the initial type and execution environments are consistent.
For our results, three consistency properties are needed:
\begin{itemize}
\item mapping consistency, written $\mapconsist{\Omega}$, guarantees a region mapping $M$ satisfies the region constraints $\Omega$% under which an expression was typed
\item local value consistency, written $\localconsist{L}{\Gamma}$, guarantees local values in $L$ have types consistent with the environment $\Gamma$ (using $M$ to map logical regions in $\Gamma$ to physical regions)
%under which the expression was typed
\item store consistency, written $\storeconsist{S}{H}$, guarantees locations in $S$ have values consistent with heap typing $H$
\end{itemize}
